\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[most]{tcolorbox}

\geometry{margin=2.5cm}
\pagestyle{fancy}
\fancyhf{}
\rhead{Computing Infrastructures}
\lhead{II Semester, 2026, Politecnico di Milano}
\cfoot{\thepage}

\newtcolorbox{key}[1]{
    colback=blue!5!white,
    colframe=blue!75!black,
    fonttitle=\bfseries,
    title=#1
}

\newtcolorbox{formula}[1]{
    colback=green!5!white,
    colframe=green!75!black,
    fonttitle=\bfseries,
    title=#1
}

\newtcolorbox{ex}{
    colback=yellow!5!white,
    colframe=orange!75!black,
    fonttitle=\bfseries,
    title=Esempio
}

\title{\textbf{Computing Infrastructures}\\
\large Riassunto completo del corso}
\author{Politecnico di Milano}
\date{A.A. 2025-2026, II Semestre}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Prefazione}
I contenuti di questo PDF sono stati compilati con il solo scopo di avere una risorsa esaustiva e facilmente consultabile degli argomenti trattati nel corso di Computing Infrastructures sostenuto dal professore Palermo: non sono in alcun modo materiale sostitutivo alle lezioni, che frequentate in presenza mi hanno permesso di capire a fondo la materia. Sconsiglio di usare esclusivamente suddetto documento per cercare di prepararsi all'esame, supporto invece l'uso di questa dispensa per fare il punto della situazione durante il periodo di studio.

\section{Datacenters}
\subsection{Introduction}
\begin{key}{Datacenter}
A Datacenter is a building whose primary purpose is to house a computer room and its support areas, so that services can run continuously and efficiently
\end{key}
There exist lots of different types of datacenters:
\begin{itemize}
\item \textbf{Enterprise Data Centers} - facilities operated and controlled by the company that provides the service. Main problem: expensive to maintain (to build or not to build dilemma) and can shorten the possibility to generate money by the business.
\item \textbf{Colocation Data Centers} - larger facilities built to accomodate different businesses and can personalize individual IT parts for individual businesses. Main problem: IT purchases are on your own and restrictions on access and maintenance. 
\item \textbf{Managed Hosting Platforms} - all facilities are managed by third parties, still a single-tenant solution. Main problem: higher operational costs and possibility of customer lock in problem.
\end{itemize}



\end{document}